High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2020-06-04 paper/main.tex
WIP paper higher order corrs write up

\subsection*{Data}
We examined two types of data: synthetic data and human functional
neuroimaging data.  We constructed and leveraged the synthetic data to
evaluate our general approach~\citep[for a related validation
approach see][]{ThomEtal18}.  Specifically, we tested how well
Equation~\ref{eqn:timecorr} could be used to recover known dynamic
correlations using different choices of kernel ($\kappa$;
Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
exhibited different temporal properties.  We applied our approach to a
functional neuroimaging dataset to test the hypothesis that ongoing
cognitive processing is reflected in high-order dynamic correlations.
We used an across-participant classification test to estimate whether
dynamic correlations of different orders contain information about
which timepoint in a story participants were listening to.

@@

@@

>>>>

\subsection*{Data}
We examined two types of data: synthetic data and human functional
neuroimaging data.  We constructed and leveraged the synthetic data to
evaluate our general approach~\citep[for a related validation
approach see][]{ThomEtal18}.  Specifically, we tested how well
Equation~\ref{eqn:timecorr} could be used to recover known dynamic
correlations using different choices of kernel ($\kappa$;
Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
exhibited different temporal properties. We also used this synthetic
data to simulate higher-order correlations and tested how well Equation~\ref{eqn:timecorr}
could recover these correlations using the best kernel from the
previous synthetic data analysis.  We applied our approach to a
functional neuroimaging dataset to test the hypothesis that ongoing
cognitive processing is reflected in high-order dynamic correlations.
We used an across-participant classification test to estimate whether
dynamic correlations of different orders contain information about
which timepoint in a story participants were listening to.

@@

\subsubsection*{Simulated higher-order correlations}
We simulated first and second order correlations reflecting the 4 qualitatively different patterns
of synthetic dynamic correlations.
 We repeated the processes 10 times for each order and for each of the 4 dynamic pattern (Constant, Random, Ramping, and
Event) explored in \textit{Synthetic data}.  First,
 we generated a timeseries of correlations which comprised 50 features (dimensions)
that varied over 300 timepoints using 1 of the 4 \textit{Synthetic data} dynamic
patterns. To calculate the next increasing order of corrrelations, ${ Y_{n+1,t}}$, we
multiplied the vectorized correlation matrix by its transpose, for
each timepoint:

\begin{align}
Y_{n+1,t} = vec(\mathbf{\Sigma}_{n,t})\cdot vec(\mathbf{\Sigma}_{n,t})^\top\label{eqn:veccorr}
  \end{align}

 Observations were then drawn at each timepoint from a  ${ Y_{n,t}}$-mean multivariate Gaussian distribution with a
covariance matrix defined as ${ Y_{n+1,t}}$.

@@

\subsection*{Recovering known higher-order dynamic correlations from synthetic data}
We generated synthetic datasets that differed in how the underlying
correlations changed over time.  For each dataset, we applied
Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
widths.  We assessed how well the true underlying correlations at each
timepoint matched the recovered correlations
(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
our approach recovered the correlation dynamics we embedded into the
data.  However, the quality of these recoveries varied across
different synthetic datasets in a kernel-dependent way.
